---
title: "openRVF pipeline notes"
author: "Nathan Layman"
date: "`r Sys.Date()`"
output: html_document
---
```{r mermaid_script, echo=FALSE, message = FALSE, results='asis'}
if(knitr::pandoc_to("html")) {
  cat('<script src="https://unpkg.com/mermaid@10/dist/mermaid.min.js"></script>')
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
h <- here::here
```

## Project pipeline

```{r mermaid, echo=FALSE, message = FALSE, results='asis'}
mer <- targets::tar_mermaid(targets_only = TRUE, 
                            outdated = FALSE,
                            legend = FALSE, 
                            color = FALSE,
                            script = h("_targets.R"))

if(knitr::pandoc_to("html")) {
  cat('<pre><div class="mermaid">', mer, '</div></pre>', sep = "\n")
} else {
  cat(
  "```mermaid",
  mer[1],
  #'Objects([""Objects""]) --- Functions>""Functions""]',
  'subgraph Project Workflow',
  mer[3:length(mer)],
  'linkStyle 0 stroke-width:0px;',
  "```",
  sep = "\n")
}

```

<details>
<summary> Error: Error installing package 'nanonext': 
</summary>
<br>

Error:
```
* installing *source* package ‘nanonext’ ...
** package ‘nanonext’ successfully unpacked and MD5 sums checked
** using staged installation
No existing 'libmbedtls' >= 2.5 found
Detecting 'cmake'...
Required 'cmake' not found
ERROR: configuration failed for package ‘nanonext’
* removing ‘/Users/nathanlayman/Documents/Academia/EHA/Projects/open-rvfcast/renv/staging/1/nanonext’
install of package 'nanonext' failed [error code 1]
```

Fix:
```
brew instal cmake
```
</details>

<details>
<summary> Error target readme: argument "store" is missing, with no default
</summary>
<br>

Error:
```
Error:
! Error running targets::tar_make()
  Error messages: targets::tar_meta(fields = error, complete_only = TRUE)
  Debugging guide: https://books.ropensci.org/targets/debugging.html
  How to ask for help: https://books.ropensci.org/targets/help.html
  Last error: argument "store" is missing, with no default
```

Fix:
```
Add store argument to tar_mermaid call in readme. Update targets to use here() for every file call. Change tar_mermaid to 

mer <- targets::tar_mermaid(targets_only = TRUE, 
                            outdated = FALSE,
                            legend = FALSE, 
                            color = FALSE,
                            script = h("_targets.R"))
                            
```    

</details>
<details>
<summary> Error target modis_ndvi_bundle_request: no applicable method for 'filter' applied to an object of class "list"
</summary>
<br>
Error:
```
✖ error target modis_ndvi_bundle_request
▶ end pipeline [2.272 hours]
Warning messages:
1: [readValues] raster has no values 
2: 1 targets produced warnings. Run targets::tar_meta(fields = warnings, complete_only = TRUE) for the messages. 
Error:
! Error running targets::tar_make()
  Error messages: targets::tar_meta(fields = error, complete_only = TRUE)
  Debugging guide: https://books.ropensci.org/targets/debugging.html
  How to ask for help: https://books.ropensci.org/targets/help.html
  Last error: no applicable method for 'filter' applied to an object of class "list"
```
Fix:
```
Modis authentication token is expired. Renew token by forcing modis_ndvi_token target to re-run.
```
</details>

</details>
<details>
<summary> Error target sentinel_ndvi_downloaded: Failed to connect to catalogue.dataspace.copernicus.eu port 80 after 15 ms: Couldn't connect to serve
</summary>
<br>

Error:
```
x errored branch sentinel_ndvi_downloaded_5cfced28d04857ef
x errored pipeline [2.254 minutes]
Warning messages:
1: There was 1 warning in `mutate()`.
ℹ In argument: `iso_code = countrycode::countrycode(country, origin =
  "country.name", destination = "iso3c")`.
Caused by warning:
! Some values were not matched unambiguously: ceuta, dominican (rep.), melilla 
2: There was 1 warning in `mutate()`.
ℹ In argument: `continent = countrycode::countrycode(country, origin =
  "country.name", destination = "continent")`.
Caused by warning:
! Some values were not matched unambiguously: ceuta, dominican (rep.), melilla 
3: [readValues] raster has no values 
4: 2 targets produced warnings. Run targets::tar_meta(fields = warnings, complete_only = TRUE) for the messages. 
Error:
! Error running targets::tar_make()
Error messages: targets::tar_meta(fields = error, complete_only = TRUE)
Debugging guide: https://books.ropensci.org/targets/debugging.html
How to ask for help: https://books.ropensci.org/targets/help.html
Last error message:
    Failed to connect to catalogue.dataspace.copernicus.eu port 80 after 15 ms: Couldn't connect to server
Last error traceback:
    download_sentinel_ndvi(sentinel_ndvi_api_parameters, download_directory ...
    GET(url, add_headers(Authorization = paste("Bearer", content(auth)$acces...
    request_perform(req, hu$handle$handle)
    request_fetch(req$output, req$url, handle)
    request_fetch.write_disk(req$output, req$url, handle)
    curl::curl_fetch_disk(url, x$path, handle = handle)
    .handleSimpleError(function (condition)  {     state$error <- build_mess...
    h(simpleError(msg, call))
```

Fix:
```
Firewalls sometimes block outbound access over port 80 for `http`. Change URL to use `https`.
There was also some authentication problems due to curl forwarding the GET request to the new
address (which happens to be https already). Updated new address to:
https://download.dataspace.copernicus.eu/odata/v1/Products
```
